Light inextensible strings under tension in the Schwarzschild geometry

### 2019-05-21 string_jpam.tex
fixes #16
fixes #13

If, conversely, $r'(\phi)>0$ whenever~$r>1$, then the string has only
one free end; the other is tangential to the event horizon, except in
the exceptional case of constant~$\phi$ when the string is radial
for~$r>1$.

@@

\begin{figure}[p] % created by "closest_approach2.R"
\centering
\includegraphics[width=170mm]{closest_approach_selfintersecting.pdf}
\caption{Self-intersecting strings arranged by closest approach to the
  event horizon which occurs at $\phi=0$.  Strings shown for $\phi\geq
  0$}
\label{closest_approach_self_intersecting}
\end{figure}

>>>>

If, conversely, $r'(\phi)>0$ whenever~$r>1$, then the string has only
one free end; the other is tangential to the event horizon (in the
sense that ${\displaystyle \lim_{r\longrightarrow 1^+}r'=0}$), except
in the exceptional case of constant~$\phi$ when the string is radial
for~$r>1$.

@@

\begin{figure}[p] % created by "closest_approach2.R"
\centering
\includegraphics[width=170mm]{closest_approach_selfintersecting.pdf}
\caption{Self-intersecting strings shown for $\phi\geq 0$.  Closest
  approach to the event horizon occurs at $\phi=0$ and
  $r\in\left(1,1.0761\right)$; strings are symmetrical about $\phi=0$}
\label{closest_approach_self_intersecting}
\end{figure}
